### 2013-02-13 exam5/1.tex
{} to [] and remove dir problem.

\begin{verbatim}
"this is JSON"
{ "this is JSON", "Jr." }
{ {}, { "So", "is" }, "this" }
\end{verbatim}
The first example is just a string.  The second is an ``array'' of two
JSON elements, which are both strings.  The third is another array,
but of three elements: the first is an array of zero elements, the
second is an array of two strings, and the third is a string.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{15}

% JSON problem

Here are data and class definitions for representing the files and
directories of a computer:

\begin{verbatim}
;; An Elem is one of
;; - (new file% String Number)
;; - (new dir% String LoElem)
(define-class file% (fields name size))
(define-class dir% (fields name elems))

;; A LoElem is one of
;; - (new mt%)
;; - (new cons% Elem LoElem)
(define-class mt%)
(define-class cons% (fields first rest))    
\end{verbatim}

\noindent
Here is an example of a directory tree and its representation as an
\verb|Elem|:
\begin{verbatim}
#|
 User
   +-- A
   |   +-- a.txt
   |   +-- B
   |       +-- b.rkt
   +-- C
       +-- c.c
|#

(define mt (new mt%))
(define a (new file% "a.txt" 5))
(define b (new file% "b.rkt" 10))
(define c (new file% "c.c" 1000))

(define C/ (new dir% "C" (new cons% c mt)))
(define B/ (new dir% "B" (new cons% b mt)))
(define A/ (new dir% "A" (new cons% a (new cons% B/ mt))))
(define User/ (new dir% "/" (new cons% A/ (new cons% C/ mt))))
\end{verbatim}

\newpage
\noindent
Your job is to implement one of the main tasks of the common Unix
utility \verb|find|, which gives a list of all the files within an
element.  To do so, add a \verb|list-files| method of \verb|Elem|
which produces a list of files.  So for example, we expect:
\begin{verbatim}
(check-expect (User/ . list-files) 
              (new cons% a (new cons% b (new cons% c mt))))
\end{verbatim}
\emph{Hint}: it may come in handy to be able to concatenate two
\verb|LoElem| together.

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi

\begin{solution}
\begin{alltt}
\rubricpts{1pts -- interfaces, contracts, purpose}
;; An Elem implements
;; - list-files : -> LoElem
;;   List all files within this element.

\rubricpts{2pts -- interfaces, contracts, purpose}
;; A LoElem implements
;; - list-files : -> LoElem
;;   List all files within this list of elements.
;; - append : LoElem -> LoElem
;;   Append this list of elements to given list.

\rubricpts{1pt -- code}
;; in dir%
(define (list-files)
  (this . elems . list-files))

\rubricpts{1pt -- code}
;; in file%
(define (list-files)
  (new cons% this (new mt%)))

\rubricpts{2pt -- code}
;; in mt%
(define (append loe) loe)
(define (list-files) this)

\rubricpts{4pt -- code}
;; in cons%
(define (append loe)
  (new cons% (this . first) (this . rest . append loe)))
(define (list-files)
  (this . first . list-files . append (this . rest . list-files)))

\rubricpts{1pt -- sanity}

\rubricpts{3pts -- tests}
;; tests
(check-expect (mt . append (new cons% a mt)) (new cons% a mt))
(check-expect ((new cons% a mt) . append (new cons% b mt))
              (new cons% a (new cons% b mt)))

(check-expect (mt . list-files) mt)
(check-expect ((new cons% a (new cons% b mt)) . list-files)
              (new cons% a (new cons% b mt)))

(check-expect (a . list-files) (new cons% a mt))
\end{alltt}
\end{solution}

\end{problem}
\newpage

>>>>

\begin{verbatim}
"this is JSON"
[ "this is JSON", "Jr." ]
[ [], [ "So", "is" ], "this" ]
\end{verbatim}
The first example is just a string.  The second is an ``array'' of two
JSON elements, which are both strings.  The third is another array,
but of three elements: the first is an array of zero elements, the
second is an array of two strings, and the third is a string.

@@
